---
title: "Dey_Review"
author: "Sristi Dey"
date: "2025-03-22"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```  

##Review of Sadiya_markdown.Rmd by Sristi Dey

Hi Sadiya, 
I found an error while running your markdown file in line 32 (could not open the connection to fang_et_al_genotypes) ```fang_et_al_genotypes <- read.delim("fang_et_al_genotypes.txt", sep = "\t", header = TRUE)```
The error did not allow me to run the markdown file ahead anymore

I suggest you to load the file directly in Rstudio and then read it into the data frame, for example:
```{r load data}
url_genotypes <- "https://raw.githubusercontent.com/EEOB-BioData/BCB546_Spring2024/refs/heads/main/assignments/UNIX_Assignment/fang_et_al_genotypes.txt"
genotypes <- read.table(url_genotypes, header = TRUE, sep = "\t", stringsAsFactors = FALSE)
```

##Plots
#Plot 1&4 - SNPs per chromosome by group/Polymorphic SNPs per chromosome by group
For this plot it would be better to read the chromosomes in order in the x-axis, below code can help you order them from 1-10, then the non-numeric chromosomes
```{r sort  using factor}
your merged maize data$Chromosome <- factor(your merged maize data$Chromosome, 
    levels = c("1", "2", "3", "4", "5", "6", "7", "8", "9", "10", "multiple", "unknown"))
```

#Plot 3
For the zygosity plots, you may want to remove the x axis text to make the plots cleaner as there's so many samples - you can use theme(axis.text.x=element_blank())

#Overview
The README file is clear, but a few sections could use more examples
The code is well-organized, but some functions might need more focus to remove errors, overall excellently done
 




